---
title: "Temporal variation in transmission during the COVID-19 outbreak in Vietnam"
bibliography: library.bib
output:
  distill::distill_article:
    self_contained: true
    toc: false
---

Data source
===
Raw data is shared and permitted to use by courtesy of [NCSC](https://covid19.ncsc.gov.vn)

Customization for Calculating Subnational Level for Vietnam
===

The submational results for Vietnam is carried out by Data Analysis team, COVID19 & Beyond Taskforce, [AVSE Global](https://avseglobal.org) with the following team members:

- [Man Tan Bui PhD](https://www.linkedin.com/in/man-bui-b2a77442) 
- Tung Thanh Pham MD
- Huong Thi Chu
- [Vang Le-Quy PhD - Team Leader](https://www.linkedin.com/in/vanglequy)

The calculation is based on the method and R packaged as mentioned in the following paper.


```{r, include = FALSE}
title <- FALSE
```

```{r, child = "_paper/title-skeleton.Rmd"}
```



**More information** For more detail and the limitations of these estimates
please see our [methods](https://epiforecasts.io/covid/methods.html)), our
[preprint](https://wellcomeopenresearch.org/articles/5-112/v1)[@rtwebsite], the
[documentation of our transmission tracking R
package](https://epiforecasts.io/EpiNow2/)[@epinow2] and the documentation of
our [R data package](https://epiforecasts.io/covidregionaldata/)
[@covidregionaldata]. Stored versions of our estimates and the code used to
generate them can be found
[here](https://github.com/epiforecasts/covid-rt-estimates).**


**Note:** Our methodology remains an area of active research so please consider
contacting us if interested in using, or evaluating, our approach. As an
open-source project we also welcome code and methodology contributions, please
see the linked code repositories for details on how to contribute.
